Dataset-level report

### 2019-11-14 analysis/reports/dat_report_template.Rmd
pull dis

loadd(all_di, cache = cache)

@@

site_samples <- all_di %>%
  select(sim, source, site, singletons) %>%
  group_by(source, site, singletons) %>%
  summarize(nsamples = length(unique(sim))) %>%
  ungroup() %>%
  filter(source == "sampled") %>%
  left_join(select(sv, -source, -sim), by = c("site", "singletons"))
```

>>>>

all_di <- readd(all_di_obs, cache = cache)

@@

site_samples <- all_di %>%
  left_join(select(sv, -source, -sim), by = c("site", "singletons"))
```
